Model Comparison

### 2020-03-14 paper/supplementary_material.Rmd
add molde comparison to suppl file

All Bayesian cognitive models were implemented in the probabilistic programming language  `WebPPL` [@dippl]. The corresponding model code can be found in the associated online repository and includes information about the prior distributions for all parameters in the model (file xxxxx). To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by item), speaker informativeness and common ground sensitivity and then passed them through the model in line with the different ways in which they can be combined and aligned. The resulting predictions come in the form of distributions of developmental trajectories for each item in the congruent and the incongruent condition. We generated model predictions for each model based on the full posterior distribution for each model parameter. Based on these model predictions, we computed the marginal likelihood of the data given each model and compared them via Bayes factors (see file `model_comparison.Rmd` in the associated online repository).

@@

@@

```{r fig4, include = T, fig.align = "center", fig.cap = "Developmental trajectories for model parameters based on the posterior distribution for (A) semantic knowlede, (B) speaker informativeness and (C) prior sensitivity. Solid lines in show the MAP estimate for each parameter. Lighter lines in (B) and (C) show 300 random draws from the posterior distributon to visualize uncertainty. (A) does not include these random draws for the sake of clarity.", fig.width=12, fig.height = 4}
ggarrange(plot_sem_know, plot_speak_opt, plot_prior , labels = c("A","B","C"), nrow = 1, widths = c(1.,1,1))
```

@@

[overview fig, all model parameters for all models]
```{r fig5, include = T, fig.align = "center", fig.cap = "Model predictions based on the integration model. Colored lines show developmental trajectories for each familiar object and condition based on 300 random draws from the model posterior distribution. Top row (blue) shows the congruent condition and the bottom row (red) shows the inconguent condition. Familiar objects are ordered based on their rated age of acquisition (left o right). Dashed black lines show smoothed conditional mean of the data with 95\\% CI (in grey).", fig.width=12, fig.height = 4}
# comb_data_binned <- comb_data%>%
#   group_by(subage, alignment, item)%>%
#   summarize(k = sum(correct), n = n())%>%
#   ungroup() %>%
#   mutate(a = 1 + k,
#          b = 1 + n - k,
#          data_mean = (a-1)/(a+b-2),
#          data_ci_lower  = qbeta(.025, a, b),
#          data_ci_upper = qbeta(.975, a, b),
#          age = factor(subage))%>%
#   select(-a,-b,-n,-k)%>%
#   left_join(aoa_ratings) %>%
#   ungroup()%>%
#   mutate(item = fct_reorder(factor(item), mean_aoa))
# 
# select_pred <- sample(1:20000, 60)
# 
# plot_prag_pred <- readRDS("../saves/model_pred_prag.rds")%>%
#   filter(iteration %in% select_pred)%>%
#   left_join(aoa_ratings) %>%
#   ungroup()%>%
#   mutate(item = fct_reorder(factor(item), mean_aoa))
# 
# 
#  saveRDS(plot_prag_pred, "../saves/plot_prag_pred.rds")

@@

```{r fig6, include = T, fig.align = "center", fig.cap = "Correlations between model predictions and data binned by year, item and condition. Vertical and horizontal error bars show 95\\% HDI. Blue diamonds show congruent condition and red ones show the incongruent condition.", fig.width=12, fig.height = 6}

# cor_prag <- readRDS("../saves/model_pred_prag.rds")%>%
#   mutate(age = as.numeric(age) + min(data_comb$age_num),
#          age = cut(age,
#                       breaks = c(2,3,4,5),
#                       labels = c(2,3,4)))%>%
#   group_by(model,alignment, item, age)%>%
#   summarise(model_mean = estimate_mode(pred),
#             model_ci_lower = hdi_lower(pred),
#             model_ci_upper = hdi_upper(pred))
# 
# cor_global <- readRDS("../saves/model_pred_global.rds")%>%
#   mutate(age = as.numeric(age) + min(data_comb$age_num),
#          age = cut(age,
#                       breaks = c(2,3,4,5),
#                       labels = c(2,3,4)))%>%
#   group_by(model, alignment, item, age)%>%
#   summarise(model_mean = estimate_mode(pred),
#             model_ci_lower = hdi_lower(pred),
#             model_ci_upper = hdi_upper(pred))
# 
# cor_flat <- readRDS("../saves/model_pred_flat.rds")%>%
#   mutate(age = as.numeric(age) + min(data_comb$age_num),
#          age = cut(age,
#                       breaks = c(2,3,4,5),
#                       labels = c(2,3,4)))%>%
#   group_by(model, alignment, item, age)%>%
#   summarise(model_mean = estimate_mode(pred),
#             model_ci_lower = hdi_lower(pred),
#             model_ci_upper = hdi_upper(pred))
# 
# cor_prior <- readRDS("../saves/model_pred_prior.rds")%>%
#   mutate(age = as.numeric(age) + min(data_comb$age_num),
#          age = cut(age,
#                       breaks = c(2,3,4,5),
#                       labels = c(2,3,4)))%>%
#   group_by(model, alignment, item, age)%>%
#   summarise(model_mean = estimate_mode(pred),
#             model_ci_lower = hdi_lower(pred),
#             model_ci_upper = hdi_upper(pred))
# 
# cor_model_pred <- bind_rows(
#    cor_prag,
#    cor_global,
#    cor_flat,
#    cor_prior
# )
# 
# 
# plot_cor_model_pred <- cor_model_pred %>%
#   left_join(
#     bind_rows(
#        binnned_data%>%mutate(model = "integration"),
#        binnned_data%>%mutate(model = "no word knowledge"),
#        binnned_data%>%mutate(model = "no common ground"),
#        binnned_data%>%mutate(model = "no mutual exclusivity")
#       )
#   )%>%
#   mutate(age = fct_recode(age, 
#                           "2" = "2-year-olds",
#                           "3" = "3-year-olds",
#                           "4" = "4-year-olds"))
#
#saveRDS(plot_cor_model_pred, "../saves/corr_model_data_pred.rds")

@@

### No word

@@

@@

```{r fig8, include = T, fig.align = "center", fig.cap = "Developmental trajectories for model parameters based on the posterior distribution for (A) semantic knowlede, (B) speaker informativeness and (C) prior sensitivity. Solid lines in show the MAP estimate for each parameter. Lighter lines in (B) and (C) show 300 random draws from the posterior distributon to visualize uncertainty. (A) does not include these random draws for the sake of clarity.", fig.width=12, fig.height = 4}
ggarrange(plot_sem_know_exp, plot_speak_opt_exp, plot_prior_exp , labels = c("A","B","C"), nrow = 1, widths = c(1.1,1,1))
```

@@

@@

>>>>

All Bayesian cognitive models were implemented in the probabilistic programming language  `WebPPL` [@dippl]. The corresponding model code can be found in the associated online repository and includes information about the prior distributions for all parameters in the model (file xxxxx). To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by item), speaker informativeness and common ground sensitivity and then passed them through the model in line with the different ways in which they can be combined and aligned. The resulting predictions come in the form of distributions of developmental trajectories for each item in the congruent and the incongruent condition.

@@

Four models, one full model, others lesions. What inforamtion do we need to make good predictions

@@

```{r fig4, include = T, fig.align = "center", fig.cap = "Developmental trajectories for model parameters based on the posterior distribution for (A) semantic knowlede, (B) speaker informativeness and (C) prior sensitivity. Solid lines in show the MAP estimate for each parameter. Lighter lines in (B) and (C) show 300 random draws from the posterior distributon to visualize uncertainty. (A) does not include these random draws for the sake of clarity.", fig.width=12, fig.height = 4}
ggarrange(plot_sem_know, plot_speak_opt, plot_prior , labels = c("A","B","C"), nrow = 1, widths = c(1.3,1,1))
```

@@

[overview fig, all model parameters for all models]
```{r fig5, include = T, fig.align = "center", fig.cap = "Predicting information integration across development. Model predictions based on the integration model. Colored lines show developmental trajectories for each familiar object and condition based on 300 random draws from the model posterior distribution. Top row (blue) shows the congruent condition and the bottom row (red) shows the inconguent condition. Familiar objects are ordered based on their rated age of acquisition (left o right). Dashed black lines show smoothed conditional mean of the data with 95\\% CI (in grey). Light dots are individual data points.", fig.width=12, fig.height = 4}
# comb_data_binned <- comb_data%>%
#   group_by(subage, alignment, item)%>%
#   summarize(k = sum(correct), n = n())%>%
#   ungroup() %>%
#   mutate(a = 1 + k,
#          b = 1 + n - k,
#          data_mean = (a-1)/(a+b-2),
#          data_ci_lower  = qbeta(.025, a, b),
#          data_ci_upper = qbeta(.975, a, b),
#          age = factor(subage))%>%
#   select(-a,-b,-n,-k)%>%
#   left_join(aoa_ratings) %>%
#   ungroup()%>%
#   mutate(item = fct_reorder(factor(item), mean_aoa))
# 
# select_pred <- sample(1:20000, 60)
# 
# plot_prag_pred <- readRDS("../saves/model_pred_prag.rds")%>%
#   filter(iteration %in% select_pred)%>%
#   left_join(aoa_ratings) %>%
#   ungroup()%>%
#   mutate(item = fct_reorder(factor(item), mean_aoa))
# 
# 
#  saveRDS(plot_prag_pred, "../saves/plot_prag_pred.rds")

@@

### No word knowledge model

### No common ground model

### No mutual exclusivity model

Compare model prediction in two ways. First is via correlations and second isvia bayes factors.

Based on these model predictions, we computed the marginal likelihood of the data given each model and compared them via Bayes factors (see file `model_comparison.Rmd` in the associated online repository).

```{r fig6, include = T, fig.align = "center", fig.cap = "Predicting information integration. Correlations between model predictions and data binned by year, item and condition. Vertical and horizontal error bars show 95\\% HDI. Blue diamonds show congruent condition and red ones show the incongruent condition.", fig.width=12, fig.height = 6}

# cor_prag <- readRDS("../saves/model_pred_prag.rds")%>%
#   mutate(age = as.numeric(age) + min(comb_data$age_num),
#          age = cut(age,
#                       breaks = c(2,3,4,5),
#                       labels = c(2,3,4)))%>%
#   group_by(model,alignment, item, age)%>%
#   summarise(model_mean = estimate_mode(pred),
#             model_ci_lower = hdi_lower(pred),
#             model_ci_upper = hdi_upper(pred))
# 
# cor_global <- readRDS("../saves/model_pred_global.rds")%>%
#   mutate(age = as.numeric(age) + min(comb_data$age_num),
#          age = cut(age,
#                       breaks = c(2,3,4,5),
#                       labels = c(2,3,4)))%>%
#   group_by(model, alignment, item, age)%>%
#   summarise(model_mean = estimate_mode(pred),
#             model_ci_lower = hdi_lower(pred),
#             model_ci_upper = hdi_upper(pred))
# 
# cor_flat <- readRDS("../saves/model_pred_flat.rds")%>%
#   mutate(age = as.numeric(age) + min(comb_data$age_num),
#          age = cut(age,
#                       breaks = c(2,3,4,5),
#                       labels = c(2,3,4)))%>%
#   group_by(model, alignment, item, age)%>%
#   summarise(model_mean = estimate_mode(pred),
#             model_ci_lower = hdi_lower(pred),
#             model_ci_upper = hdi_upper(pred))
# 
# cor_prior <- readRDS("../saves/model_pred_prior.rds")%>%
#   mutate(age = as.numeric(age) + min(comb_data$age_num),
#          age = cut(age,
#                       breaks = c(2,3,4,5),
#                       labels = c(2,3,4)))%>%
#   group_by(model, alignment, item, age)%>%
#   summarise(model_mean = estimate_mode(pred),
#             model_ci_lower = hdi_lower(pred),
#             model_ci_upper = hdi_upper(pred))
# 
# cor_model_pred <- bind_rows(
#    cor_prag,
#    cor_global,
#    cor_flat,
#    cor_prior
# )
# 
# 
# plot_cor_model_pred <- cor_model_pred %>%
#   left_join(
#     bind_rows(
#        binnned_data%>%mutate(model = "integration"),
#        binnned_data%>%mutate(model = "no word knowledge"),
#        binnned_data%>%mutate(model = "no common ground"),
#        binnned_data%>%mutate(model = "no mutual exclusivity")
#       )
#   )%>%
  # mutate(age = fct_recode(age,
  #                         "2-year-olds" = "2",
  #                         "3-year-olds" = "3",
  #                         "4-year-olds" = "4"))
#
#saveRDS(plot_cor_model_pred, "../saves/corr_model_data_pred.rds")

@@

```{r table3}
model_comp_pred <- readRDS("../saves/pred_model_comparison.rds")%>%
  mutate(model = factor(model),
         `Model comparison` = fct_recode(model, 
                            "integration vs no word knowledge" = "prag_vs_global",
                            "integration vs no common ground" = "prag_vs_flat",
                            "integration vs no mutual exclusivity" = "prag_vs_prior",
                            "no word knowledge vs no mutual exclusivity" = "global_vs_flat",
                            "no word knowledge vs no common ground" = "global_vs_prior",
                            "no mutual exclusivity vs no common ground" = "flat_vs_prior"),
        `Bayes factor` = format(round(exp(logBF),2), trim = T, justify = "right", digits = 2))%>%
  select(-logBF, -model)

knitr::kable(model_comp_pred, caption = "Model comparison using Bayes factors computed based on the marginal likelihood of each model given the data.", digits = 2)
```

@@

answer the question: which is the best way to think about information integration

@@

```{r fig8, include = T, fig.align = "center", fig.cap = "Developmental trajectories for model parameters based on the posterior distribution for (A) semantic knowlede, (B) speaker informativeness and (C) prior sensitivity. Solid lines in show the MAP estimate for each parameter. Lighter lines in (B) and (C) show 300 random draws from the posterior distributon to visualize uncertainty. (A) does not include these random draws for the sake of clarity.", fig.width=12, fig.height = 4}
ggarrange(plot_sem_know_exp, plot_speak_opt_exp, plot_prior_exp , labels = c("A","B","C"), nrow = 1, widths = c(1.3,1,1))
```

@@

```{r fig9, include = T, fig.align = "center", fig.cap = "Explaining information integration across development. Model predictions based on the integration model. Colored lines show developmental trajectories for each familiar object and condition based on 300 random draws from the model posterior distribution. Top row (blue) shows the congruent condition and the bottom row (red) shows the inconguent condition. Familiar objects are ordered based on their rated age of acquisition (left o right). Dashed black lines show smoothed conditional mean of the data with 95\\% CI (in grey). Light dots are individual data points.", fig.width=12, fig.height = 4}

# select_exp <- sample(1:20000, 50)
# 
# plot_prag_exp <- readRDS("../saves/model_pred_prag_fb.rds")%>%
#   filter(iteration %in% select_pred)%>%
#   left_join(aoa_ratings) %>%
#   ungroup()%>%
#   mutate(item = fct_reorder(factor(item), mean_aoa))
# 
# 
# saveRDS(plot_prag_exp, "../saves/plot_prag_exp.rds")

plot_prag_exp<- readRDS( "../saves/plot_prag_exp.rds")

ggplot(data = comb_data, aes(x = age_num, y = correct)) +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(col = "black", height = .025, alpha = .1)+
  #geom_pointrange(data = comb_data_binned, aes(x = subage+.5, y = data_mean, ymin =data_ci_lower, ymax = data_ci_upper), stroke = 1, pch = 5)+
  #geom_line(data = comb_data_binned, aes(x = subage+.5, y = data_mean))+
  geom_line(data = plot_prag_exp, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)), size = .2, alpha = .25)+
  geom_smooth(data = comb_data, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .4, lty = 2, size = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F, col = F)+ 
  scale_colour_ptol(name = NULL)
```

@@

```{r fig10, include = T, fig.align = "center", fig.cap = "Explaining information integration. Correlations between model predictions and data binned by year, item and condition. Vertical and horizontal error bars show 95\\% HDI. Blue diamonds show congruent condition and red ones show the incongruent condition.", fig.width=12, fig.height = 6}

# cor_prag_exp <- readRDS("../saves/model_pred_prag_fb.rds")%>%
#   mutate(age = as.numeric(age) + min(comb_data$age_num),
#          age = cut(age,
#                       breaks = c(2,3,4,5),
#                       labels = c(2,3,4)))%>%
#   group_by(model,alignment, item, age)%>%
#   summarise(model_mean = estimate_mode(pred),
#             model_ci_lower = hdi_lower(pred),
#             model_ci_upper = hdi_upper(pred))
# 
# cor_mix_exp <- readRDS("../saves/model_pred_mm.rds")%>%
#   mutate(age = as.numeric(age) + min(comb_data$age_num),
#          age = cut(age,
#                       breaks = c(2,3,4,5),
#                       labels = c(2,3,4)))%>%
#   group_by(model, alignment, item, age)%>%
#   summarise(model_mean = estimate_mode(pred),
#             model_ci_lower = hdi_lower(pred),
#             model_ci_upper = hdi_upper(pred))
# 
# cor_dev_mix_exp <- readRDS("../saves/model_pred_dmm.rds")%>%
#   mutate(age = as.numeric(age) + min(comb_data$age_num),
#          age = cut(age,
#                       breaks = c(2,3,4,5),
#                       labels = c(2,3,4)))%>%
#   group_by(model, alignment, item, age)%>%
#   summarise(model_mean = estimate_mode(pred),
#             model_ci_lower = hdi_lower(pred),
#             model_ci_upper = hdi_upper(pred))
# 
# 
# cor_model_exp <- bind_rows(
#    cor_prag_exp%>%ungroup()%>%mutate(model = "integration"),
#    cor_mix_exp%>%ungroup()%>%mutate(model = "mixture"),
#    cor_dev_mix_exp%>%ungroup()%>%mutate(model = "developmental mixture")
# )
# 
# 
# plot_cor_model_exp <- cor_model_exp %>%
#   left_join(
#     bind_rows(
#        comb_data_binned%>%mutate(model = "integration"),
#        comb_data_binned%>%mutate(model = "mixture"),
#        comb_data_binned%>%mutate(model = "developmental mixture")
#       )
#   )%>%
#   mutate(age = fct_recode(age,
#                           "2-year-olds" = "2",
#                           "3-year-olds" = "3",
#                           "4-year-olds" = "4"))
# 
# saveRDS(plot_cor_model_exp, "../saves/corr_model_data_exp.rds")

plot_cor_model_exp <- readRDS( "../saves/corr_model_data_exp.rds")

ggplot(data = plot_cor_model_exp,aes(x = model_mean, y = data_mean, col = alignment)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
  geom_point(size = 1.5, stroke = 1, pch = 5)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(age~model)+
  theme_few() + 
  scale_colour_ptol(name ="Condition")

```{r table4}
model_comp_pred <- readRDS("../saves/expl_model_comparison.rds")%>%
  mutate(model = factor(model),
         `Model comparison` = fct_recode(model, 
                            "integration (explanation) vs integration (prediction)" = "fb_vs_free",
                            "integration (explanation) vs mixture" = "fb_vs_mixture",
                            "integration (prediction) vs mixture" = "free_vs_mixture",
                            "integration (explanation) vs developmental mixture" = "fb_vs_dev_mixture",
                            "integration (prediction) vs developmental mixture" = "free_vs_dev_mixture",
                            "developmental mixture vs mixture" = "dev_mixture_vs_mixture"),
        `Bayes factor` = format(round(exp(logBF)), trim = T, justify = "right", scientific = F))%>%
  select(-logBF, -model)

knitr::kable(model_comp_pred, caption = "Model comparison using Bayes factors computed based on the marginal likelihood of each model given the data.", digits = 2)
```

### 2020-03-14 stats/model_comparison.Rmd
add molde comparison to suppl file

model_comp <- bind_rows(

@@

  readRDS("../saves/model_pred_prior.rds") %>%
    right_join(d_model_comp.summarized)%>%
    select(model,chain,iteration, age, alignment,item,pred, n, k)
) %>%
  mutate(
    log_like = dbinom(x = k, size = n, prob = pred, log = TRUE)
  ) %>%
  group_by(chain, model, iteration) %>%
  summarize(total_likelihood_sample = sum(log_like)) %>%
  group_by(chain, model) %>%
  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
  spread(model, marginal_likelihood)%>%
  mutate(prag_vs_global = pragmatic - global, # subtract likelihood for each predictions and model
         prag_vs_flat= pragmatic - flat,
         prag_vs_prior= pragmatic - prior,
         global_vs_flat = global - flat,
         global_vs_prior = global - prior,
         flat_vs_prior = flat - prior) %>%
  select(-pragmatic, -global, -flat, - prior) %>%
  gather(model, logBF, -chain)

@@

# compare models
model_comp <- model_like %>%
  na.omit(chain)%>%
  group_by(model) %>%
  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
  spread(model, marginal_likelihood)%>%
  mutate(fb_vs_free = fullBayes - pragmatic,
          fb_vs_mixture= fullBayes - mixture,
         fb_vs_dev_mixture= fullBayes - dev_mixture,
          free_vs_mixture = pragmatic - mixture,
         free_vs_dev_mixture = pragmatic - dev_mixture,
         dev_mixture_vs_mixture = dev_mixture - mixture
         ) %>%
  select(-pragmatic, -fullBayes, -mixture, -dev_mixture) %>%
  gather(model, logBF)

>>>>

@@

  readRDS("../saves/model_pred_prior.rds") %>%
    right_join(d_model_comp.summarized)%>%
    select(model,chain,iteration, age, alignment,item,pred, n, k)
) %>%
  mutate(
    log_like = dbinom(x = k, size = n, prob = pred, log = TRUE)
  ) %>%
  group_by(chain, model, iteration) %>%
  summarize(total_likelihood_sample = sum(log_like))

model_by_chain <- model_like %>%
  na.omit(chain)%>%
  group_by(chain, model) %>%
  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
  spread(model, marginal_likelihood)

saveRDS(model_by_chain, "../saves/pred_model_likelihood_chain.rds")

model <- model_like %>%
  na.omit(chain)%>%
  group_by(model) %>%
  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample))

saveRDS(model, "../saves/pred_model_likelihood.rds")

model_comp <- model_like  %>%
  na.omit(chain)%>%
  group_by(model) %>%
  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample))%>%
  spread(model, marginal_likelihood)%>%
  mutate(prag_vs_global = pragmatic - global, # subtract likelihood for each predictions and model
         prag_vs_flat= pragmatic - flat,
         prag_vs_prior= pragmatic - prior,
         global_vs_flat = global - flat,
         global_vs_prior = global - prior,
         flat_vs_prior = flat - prior) %>%
  select(-pragmatic, -global, -flat, - prior) %>%
  gather(model, logBF)

saveRDS(model_comp, "../saves/pred_model_comparison.rds")

@@

model <- model_like %>%
  na.omit(chain)%>%
  group_by(model) %>%
  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample))

saveRDS(model, "../saves/expl_model_likelihood.rds")

model_comp <- model_like  %>%
  na.omit(chain)%>%
  group_by(model) %>%
  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample))%>%
  spread(model, marginal_likelihood)%>%
  mutate(fb_vs_free = fullBayes - pragmatic,
          fb_vs_mixture= fullBayes - mixture,
         fb_vs_dev_mixture= fullBayes - dev_mixture,
          free_vs_mixture = pragmatic - mixture,
         free_vs_dev_mixture = pragmatic - dev_mixture,
         dev_mixture_vs_mixture = dev_mixture - mixture
         ) %>%
  select(-pragmatic, -fullBayes, -mixture, -dev_mixture) %>%
  gather(model, logBF)
